### 2017-09-17 reports/thesis/book.tex
In thesis, added more on detectors.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \emph{Source: G.~Michael (2001) \citep{michael2001x}}}
\label{fig:x_ray_tube}
\end{figure}

Bremsstrahlung radiation is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target. The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation. As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
\caption{A typical energy spectrum of photons emitted from an X-ray tube. The continuous spectrum is the result of Bremmsstrahlung radiation. The peaks are the result of characteristic radiation. \emph{Source: G.~Michael (2001) \citep{michael2001x}}}
\label{fig:x_ray_spectrum}
\end{figure}

@@

\subsection{Detection and Reconstruction}
Most X-ray detectors are scintillator-photodiode detectors. The photons interact with the scintiallator material and produce visible light. The visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}. The detectors used in CT scanning are flat bed scanner which consist of an array of panels of photodiodes \citep{cantatore2011introduction}.

@@

Studies have been done to use x-ray CT to do defection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}. This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}. Voids then can be classified as defects if the voids are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.

@@

The grey values of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector. When the photons interact with the scintillator, they are converted into visible light. The visible light photons are then detected and converted into a grey value. How the detected visible light is converted is important in modelling the grey value.

Should the grey value be proportional to the number of photons detected, the detector is known as a quantum counter and the grey value is a Poisson random variable, up to a constant \citep{whiting2006properties}. However if the grey value records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector. The grey value has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}. There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \citep{michael2001x}}
\label{fig:x_ray_tube}
\end{figure}

Bremsstrahlung is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target. The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation. As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
\caption{A typical energy spectrum of photons emitted from an X-ray tube. The continuous spectrum is the result of bremmsstrahlung. The peaks are the result of characteristic radiation. \citep{michael2001x}}
\label{fig:x_ray_spectrum}
\end{figure}

@@

\subsection{Detection}
Most X-ray detectors are made up of a scintillator material \citep{greskovich1997ceramic} and photodiodes. Firstly the x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}. Lastly the visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}. Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.

The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}. The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}. The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image on a computer \citep{cierniak2011x}.

@@

Studies have been done to use x-ray CT to do defection detection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}. This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}. Voids then can be classified as defects if the voids are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.

@@

The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector. When the photons interact with the scintillator, they are converted into visible light. The visible light photons are then detected and converted into a greyvalue. How the detected visible light is converted is important in modelling the greyvalue.

Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}. However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector. The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}. There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.
